Robust positively invariant sets for state dependent and scaled disturbances

### 2015-08-02 postreview.tex
Added file to accommodate reviews.
Made changes according to review 16643

	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=0}^{k-1}v_{l,i}^\ast(x)

@@

	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} 

@@

compact on any compact set $\mathcal S\subset\mathbb R^n$.

The proof has two main steps: First we prove that $\mathcal X_p$ is compact for $p\leq n$
where $n$ is the dimension of the state $x$. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
finite $N$ such that $\mathcal C\subseteq D_{N}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{N}$ and deducing that $\mathcal X^\infty = \mathcal X_N$.

@@

the set $\mathcal X_{n}$ is also bounded. To show that $D_k$ grows exponentially we use the compactness 

@@

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\biggl(\bigoplus_{i\leq k-1} 

@@

\bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 

@@

We have seen that we can compute a the maximal robust positively invariant set $\mathcal X^\infty$ for linear 

@@

In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic 

>>>>

	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=1}^{k-1}v_{l,i}^\ast(x)

@@

	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{1 \leq i\leq l-1}{\bigominus} 

@@

bounded on any bounded set $\mathcal S\subset\mathbb R^n$.

The proof has two main steps: First we prove that $\mathcal X_p$ is bounded for $p\leq n$
where $n$ is the dimension of the state $x$. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
the set $D_k$ grows exponentially, i.e. that for any given bounded set $\mathcal C$ there exists
finite $N$ such that $\mathcal C\subseteq D_{N}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{N}$ and deducing that $\mathcal X^\infty = \mathcal X_N$.

@@

the set $\mathcal X_{n}$ is also bounded. To show that $D_k$ grows exponentially we use the boundedness 

@@

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\biggl(\bigoplus_{1\leq i\leq k-1} 

@@

\bigoplus_{1\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 

@@

We have seen that we can compute the maximal robust positively invariant set $\mathcal X^\infty$ for linear 

@@

In this section we discuss the calculation of the MRPI set for a linearised and simplified model of the magnetic 
